TBD

### 2016-08-31 paper/paper.tex
+ more related work

\section{Experiments}
\section{Related Works}
Robustness analyses: \cite{DBLP:conf/hybrid/WangGRJF16}

Stability analyses of closed loop systems: \cite{DBLP:conf/hybrid/RouxJG15}.
This analysis is performed in the state space
domain using Lyapunov-based quadratic invariants.
\section{Conclusions}

>>>>

\section{Experiments}
\section{Related Works}
Robustness analyses of closed-loop systems: \cite{DBLP:conf/hybrid/WangGRJF16}.
The approach relies on an invariant computation
on the discrete system dynamics.

Stability analyses of closed loop systems: \cite{DBLP:conf/hybrid/RouxJG15}.
This analysis is performed in the state space
domain using Lyapunov-based quadratic invariants.

Synthesis of switching
controllers for stabilizing continuous-time plants: \cite{DBLP:conf/cdc/RavanbakhshS15}

\section{Conclusions}
